---
title: "RP result"
author: "Shanshan Hu"
date: "7/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggthemes)
library(glmnet) # ridge and lasso
library(gam) # for gam
library(pls) # pcr pls
library(leaps) # regsubset
library(MASS) # lda qda
library(class) # knn
library(caret) # knn with prob
library(gbm) # boosting
library(boot) # cross validation
library(car) # vif, residual plots, partial residual plots
library (ROCR) 
library (pROC) # ROC AUC plot
library(tree)
library(randomForest)
library(ranger) # Random Forest
library(neuralnet) # DNN
library(e1071) # SVM
library(RandPro) # Random Projection Method 1

library(pryr) # memory count
library(MatrixModels) # sparse matrix representation
```

```{r}
setwd("D:\\Merck challenge\\qsar_train")
df1_x = read_csv("D:\\Merck challenge\\qsar_train\\QSAR_6_train_x.csv") 
df1_y = read_csv("D:\\Merck challenge\\qsar_train\\QSAR_6_train_y.csv") 
df1=cbind(df1_y,df1_x)
```

# Random Projection
```{r}
# dimensionality
d=c(0.1,0.3,0.5,0.7)
dim=dimension(nrow(df1_x), epsilon = d)
dim
```

# Output for random projection matrix, transformation matrix and processing time. 
```{r}
rp.csv <- function(ncols,epsilon,method="gaussian",fname,rfname){
  ptm = proc.time()
  rp11=form_matrix(ncol(df1_x), ncols, FALSE, eps = epsilon, projection = method)
  rrp11=as.matrix(df1_x)%*%rp11
  write.csv(rp11,fname)
  write.csv(rrp11,rfname)
  rp11df=cbind(df1_y,rrp11)
  time_spent = proc.time() - ptm
  paste("Processing time:", round(time_spent[3]),"seconds")
  return (time_spent)
  }
```
# Gaussian Dimension:1169 Epsilon:0.3
```{r}
set.seed(1)
rp.csv(1169,0.3,"gaussian","6rp1g3.csv","result6rp1g3.csv")
rp.csv(1169,0.3,"gaussian","6rp2g3.csv","result6rp2g3.csv")
rp.csv(1169,0.3,"gaussian","6rp3g3.csv","result6rp3g3.csv")
rp.csv(1169,0.3,"gaussian","6rp4g3.csv","result6rp4g3.csv")
rp.csv(1169,0.3,"gaussian","6rp5g3.csv","result6rp5g3.csv")
```
# Gaussian Dimension:505 Epsilon:0.5
```{r}
set.seed(1)
rp.csv(505,0.5,"gaussian","6rp1g5.csv","result6rp1g5.csv")
rp.csv(505,0.5,"gaussian","6rp2g5.csv","result6rp2g5.csv")
rp.csv(505,0.5,"gaussian","6rp3g5.csv","result6rp3g5.csv")
rp.csv(505,0.5,"gaussian","6rp4g5.csv","result6rp4g5.csv")
rp.csv(505,0.5,"gaussian","6rp5g5.csv","result6rp5g5.csv")
```   
# Gaussian Dimension:322 Epsilon:0.7
```{r}
set.seed(1)
rp.csv(322,0.7,"gaussian","6rp1g7.csv","result6rp1g7.csv")
rp.csv(322,0.7,"gaussian","6rp2g7.csv","result6rp2g7.csv")
rp.csv(322,0.7,"gaussian","6rp3g7.csv","result6rp3g7.csv")
rp.csv(322,0.7,"gaussian","6rp4g7.csv","result6rp4g7.csv")
rp.csv(322,0.7,"gaussian","6rp5g7.csv","result6rp5g7.csv")
```
# Probability Dimension:1169 Epsilon:0.3
```{r}
set.seed(1)
rp.csv(1169,0.3,"probability","6rp1p3.csv","result6rp1p3.csv")
rp.csv(1169,0.3,"probability","6rp2p3.csv","result6rp2p3.csv")
rp.csv(1169,0.3,"probability","6rp3p3.csv","result6rp3p3.csv")
rp.csv(1169,0.3,"probability","6rp4p3.csv","result6rp4p3.csv")
rp.csv(1169,0.3,"probability","6rp5p3.csv","result6rp5p3.csv")
```
#  Probability Dimension:505 Epsilon:0.5
```{r}
set.seed(1)
rp.csv(505,0.5,"probability","6rp1p5.csv","result6rp1p5.csv")
rp.csv(505,0.5,"probability","6rp2p5.csv","result6rp2p5.csv")
rp.csv(505,0.5,"probability","6rp3p5.csv","result6rp3p5.csv")
rp.csv(505,0.5,"probability","6rp4p5.csv","result6rp4p5.csv")
rp.csv(505,0.5,"probability","6rp5p5.csv","result6rp5p5.csv")
```   
# Probability Dimension:322 Epsilon:0.7
```{r}
set.seed(1)
rp.csv(322,0.7,"probability","6rp1p7.csv","result6rp1p7.csv")
rp.csv(322,0.7,"probability","6rp2p7.csv","result6rp2p7.csv")
rp.csv(322,0.7,"probability","6rp3p7.csv","result6rp3p7.csv")
rp.csv(322,0.7,"probability","6rp4p7.csv","result6rp4p7.csv")
rp.csv(322,0.7,"probability","6rp5p7.csv","result6rp5p7.csv")
```
# Achlioptas Dimension:1169 Epsilon:0.3
```{r}
set.seed(1)
rp.csv(1169,0.3,"achlioptas","6rp1a3.csv","result6rp1a3.csv")
rp.csv(1169,0.3,"achlioptas","6rp2a3.csv","result6rp2a3.csv")
rp.csv(1169,0.3,"achlioptas","6rp3a3.csv","result6rp3a3.csv")
rp.csv(1169,0.3,"achlioptas","6rp4a3.csv","result6rp4a3.csv")
rp.csv(1169,0.3,"achlioptas","6rp5a3.csv","result6rp5a3.csv")
```
# Achlioptas Dimension:505 Epsilon:0.5
```{r}
set.seed(1)
rp.csv(505,0.5,"achlioptas","6rp1a5.csv","result6rp1a5.csv")
rp.csv(505,0.5,"achlioptas","6rp2a5.csv","result6rp2a5.csv")
rp.csv(505,0.5,"achlioptas","6rp3a5.csv","result6rp3a5.csv")
rp.csv(505,0.5,"achlioptas","6rp4a5.csv","result6rp4a5.csv")
rp.csv(505,0.5,"achlioptas","6rp5a5.csv","result6rp5a5.csv")
```   
# Achlioptas Dimension:322 Epsilon:0.7
```{r}
set.seed(1)
rp.csv(322,0.7,"achlioptas","6rp1a7.csv","result6rp1a7.csv")
rp.csv(322,0.7,"achlioptas","6rp2a7.csv","result6rp2a7.csv")
rp.csv(322,0.7,"achlioptas","6rp3a7.csv","result6rp3a7.csv")
rp.csv(322,0.7,"achlioptas","6rp4a7.csv","result6rp4a7.csv")
rp.csv(322,0.7,"achlioptas","6rp5a7.csv","result6rp5a7.csv")
```

