---
title: '0607'
author: "Shanshan Hu"
date: "6/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggthemes)
library(glmnet) # ridge and lasso
library(gam) # for gam
library(pls) # pcr pls
library(leaps) # regsubset
library(MASS) # lda qda
library(class) # knn
library(caret) # knn with prob
library(gbm) # boosting
library(boot) # cross validation
library(car) # vif, residual plots, partial residual plots
library (ROCR) 
library (pROC) # ROC AUC plot
library(tree)
library(randomForest)
library(ranger) # Random Forest
library(neuralnet) # DNN
library(e1071) # SVM
library(RandPro) # Random Projection Method 1

library(pryr) # memory count
library(MatrixModels) # sparse matrix representation
```

```{r}
setwd("D:\\Merck challenge\\qsar_train")
df1_x = read_csv("D:\\Merck challenge\\qsar_train\\QSAR_15_train_x.csv") 
df1_y = read_csv("D:\\Merck challenge\\qsar_train\\QSAR_15_train_y.csv") 
df1=cbind(df1_y,df1_x)
# View column summary
summary(factor(df1$x1))

## Sparse matrix represetation
set.seed(1)
pryr::object_size(df1)
idx <- sample(nrow(df1), 1/5 * nrow(df1))
df1tr <- df1[-idx, ]
df1t <- df1[idx, ]

df1tr_m=as.matrix(df1tr)
df1trs =  as(df1tr_m,"sparseMatrix")
df1t_m=as.matrix(df1t)
df1ts =  as(df1t_m,"sparseMatrix")
pryr::object_size(df1trs)
pryr::object_size(df1ts)

## Random Forest
# CV1
set.seed(1)
ptm = proc.time()
rfmod = ranger(dependent.variable.name = "y",data=df1trs)
time_spent = proc.time() - ptm
paste("Processing time:", round(time_spent[3]),"seconds")

preds <- predict(rfmod, data = df1ts)
rmse1 <- sqrt(sum((preds$predictions - df1t$y)^2)/length(preds$predictions))
rmse1
1-sum((preds$predictions - df1t$y)^2)/sum((df1t$y - mean(df1t$y))^2)
```

```{r}
# CV2
set.seed(1)
idx2 <- sample(nrow(df1tr), 1/4 * nrow(df1tr))
df1ttr <- rbind(df1t,df1tr[-idx2,])
df1trt <- df1tr[idx2, ]

df1tr_m=as.matrix(df1ttr)
df1trs =  as(df1tr_m,"sparseMatrix")
df1t_m=as.matrix(df1trt)
df1ts =  as(df1t_m,"sparseMatrix")

ptm = proc.time()
rfmod = ranger(dependent.variable.name = "y",data=df1trs)
time_spent = proc.time() - ptm
paste("Processing time:", round(time_spent[3]),"seconds")

preds <- predict(rfmod, data = df1ts)
rmse2 <- sqrt(sum((preds$predictions - df1trt$y)^2)/length(preds$predictions))
rmse2
1-sum((preds$predictions - df1trt$y)^2)/sum((df1trt$y - mean(df1trt$y))^2)
```

```{r}
# CV3
set.seed(1)
cv3<-df1tr[-idx2,]
idx3 <- sample(nrow(cv3), 1/3 * nrow(cv3))
df1ttrtr <- rbind(df1trt,cv3[-idx3,])
df1trtt <- cv3[idx3,]

df1tr_m=as.matrix(df1ttrtr)
df1trs =  as(df1tr_m,"sparseMatrix")
df1t_m=as.matrix(df1trtt)
df1ts =  as(df1t_m,"sparseMatrix")

ptm = proc.time()
rfmod = ranger(dependent.variable.name = "y",data=df1trs)
time_spent = proc.time() - ptm
paste("Processing time:", round(time_spent[3]),"seconds")

preds <- predict(rfmod, data = df1ts)
rmse3 <- sqrt(sum((preds$predictions - df1trtt$y)^2)/length(preds$predictions))
rmse3
1-sum((preds$predictions - df1trtt$y)^2)/sum((df1trtt$y - mean(df1trtt$y))^2)
```
```{r}
# CV4
set.seed(1)
cv4<-cv3[-idx3,]
idx4 <- sample(nrow(cv4), 1/2 * nrow(cv4))
df1trtttr <- rbind(df1trtt,cv4[-idx4,])
df1ttrtrt <- cv4[idx4,]

df1tr_m=as.matrix(df1trtttr)
df1trs =  as(df1tr_m,"sparseMatrix")
df1t_m=as.matrix(df1ttrtrt)
df1ts =  as(df1t_m,"sparseMatrix")

ptm = proc.time()
rfmod = ranger(dependent.variable.name = "y",data=df1trs)
time_spent = proc.time() - ptm
paste("Processing time:", round(time_spent[3]),"seconds")

preds <- predict(rfmod, data = df1ts)
rmse4 <- sqrt(sum((preds$predictions - df1ttrtrt$y)^2)/length(preds$predictions))
rmse4
1-sum((preds$predictions - df1ttrtrt$y)^2)/sum((df1ttrtrt$y - mean(df1ttrtrt$y))^2)
```
```{r}
# CV5
set.seed(1)
cv5<-cv4[-idx4,]
idx5 <- sample(nrow(cv5), 1/2 * nrow(cv5))
df1trtttrtr <- rbind(df1ttrtrt,cv5[-idx5,])
df1ttrtrtt <- cv5[idx5,]

df1tr_m=as.matrix(df1trtttrtr)
df1trs =  as(df1tr_m,"sparseMatrix")
df1t_m=as.matrix(df1ttrtrtt)
df1ts =  as(df1t_m,"sparseMatrix")

ptm = proc.time()
rfmod = ranger(dependent.variable.name = "y",data=df1trs)
time_spent = proc.time() - ptm
paste("Processing time:", round(time_spent[3]),"seconds")

preds <- predict(rfmod, data = df1ts)
rmse5 <- sqrt(sum((preds$predictions - df1ttrtrtt$y)^2)/length(preds$predictions))
rmse5
1-sum((preds$predictions - df1ttrtrtt$y)^2)/sum((df1ttrtrtt$y - mean(df1ttrtrtt$y))^2)
# error cross-validated
(rmse1+rmse2+rmse3+rmse4+rmse5)/5
```

## Random Projection
```{r}
# dimensionality
d=c(0.1,0.3,0.5,0.7)
dim=dimension(nrow(df1_x), epsilon = d)
dim
```

Processing time for random projection. And processing time and cross-validated error rate for one iteration of random forest.
```{r}
set.seed(1)
ptm = proc.time()
rp1=form_matrix(ncol(df1_x), 897, FALSE, eps = 0.3, projection = "gaussian")
rrp1=as.matrix(df1_x)%*%rp1
time_spent = proc.time() - ptm
paste("Random Projection time:", round(time_spent[3]),"seconds")
# write.csv(rp1,"2rp1g3.csv")
# write.csv(rrp1,"result2rp1g3.csv")
pryr::object_size(rp1)

set.seed(1)
rp1df=cbind(df1_y,rrp1)
ptm = proc.time()
rfmod_rp = ranger(dependent.variable.name = "y",data=rp1df)
time_spent = proc.time() - ptm
paste("Random Forest one iteration time:", round(time_spent[3]),"seconds")

rfcv=rfcv(rrp1,rp1df$y,cv.fold = 5)
rfcv$error.cv
#with(rfcv, plot(n.var, error.cv, type="b", col="red"))
```

Function of cross-validated error rate for one iteration of random forest.
```{r}
rp.cverror <- function(ncols,epsilon,method="gaussian",fname,rfname){
  rp11=form_matrix(ncol(df1_x), ncols, FALSE, eps = epsilon, projection = method)
  rrp11=as.matrix(df1_x)%*%rp11
  write.csv(rp11,fname)
  write.csv(rrp11,rfname)
  rp11df=cbind(df1_y,rrp11)
  ptm = proc.time()
  rfmod_rp = ranger(dependent.variable.name = "y",data=rp11df)
  time_spent = proc.time() - ptm
  paste("Processing time:", round(time_spent[3]),"seconds")

  rfcv2=rfcv(rrp11,rp11df$y,cv.fold = 5)
  return(rfcv2$error.cv)
  }
```

```{r}
# rp1df=cbind(df1_y,rp1)
# idx <- sample(nrow(rp1df), 1/5 * nrow(rp1df))
# rp1tr <- rp1df[-idx, ]
# rp1t <- rp1df[idx, ]
# ptm = proc.time()
# rfmod_rp = ranger(dependent.variable.name = "y",data=rp1tr)
# time_spent = proc.time() - ptm
# paste("Processing time:", round(time_spent[3]),"seconds")
# 
# preds_rp <- predict(rfmod_rp, data = rp1t)
# rmse_rp <- sqrt(sum((preds_rp$predictions - rp1t$y)^2)/length(preds_rp$predictions))
# rmse_rp
# sum((preds_rp$predictions - rp1t$y)^2)/sum((rp1t$y - mean(rp1t$y))^2)
```

# Gaussian Dimension:1008 Epsilon:0.3
```{r}
set.seed(1)
rfcv$error.cv
rp.cverror(1008,0.3,"gaussian","2rp2g3.csv","result2rp2g3.csv")
rp.cverror(1008,0.3,"gaussian","2rp3g3.csv","result2rp3g3.csv")
rp.cverror(1008,0.3,"gaussian","2rp4g3.csv","result2rp4g3.csv")
rp.cverror(1008,0.3,"gaussian","2rp5g3.csv","result2rp5g3.csv")
```
# Gaussian Dimension:277 Epsilon:0.7
```{r}
set.seed(1)
rp.cverror(277,0.7,"gaussian","2rp1g7.csv","result2rp1g7.csv")
rp.cverror(277,0.7,"gaussian","2rp2g7.csv","result2rp2g7.csv")
rp.cverror(277,0.7,"gaussian","2rp3g7.csv","result2rp3g7.csv")
rp.cverror(277,0.7,"gaussian","2rp4g7.csv","result2rp4g7.csv")
rp.cverror(277,0.7,"gaussian","2rp5g7.csv","result2rp5g7.csv")
```
# Probability Dimension:1008 Epsilon:0.3
```{r}
set.seed(1)
rp.cverror(1008,0.3,"probability","2rp1p3.csv","result2rp1p3.csv")
rp.cverror(1008,0.3,"probability","2rp2p3.csv","result2rp2p3.csv")
rp.cverror(1008,0.3,"probability","2rp3p3.csv","result2rp3p3.csv")
rp.cverror(1008,0.3,"probability","2rp4p3.csv","result2rp4p3.csv")
rp.cverror(1008,0.3,"probability","2rp5p3.csv","result2rp5p3.csv")
```
# Probability Dimension:277 Epsilon:0.7
```{r}
set.seed(1)
rp.cverror(277,0.7,"probability","2rp1p7.csv","result2rp1p7.csv")
rp.cverror(277,0.7,"probability","2rp2p7.csv","result2rp2p7.csv")
rp.cverror(277,0.7,"probability","2rp3p7.csv","result2rp3p7.csv")
rp.cverror(277,0.7,"probability","2rp4p7.csv","result2rp4p7.csv")
rp.cverror(277,0.7,"probability","2rp5p7.csv","result2rp5p7.csv")
```
# Achlioptas Dimension:1008 Epsilon:0.3
```{r}
set.seed(1)
rp.cverror(1008,0.3,"achlioptas","2rp1a3.csv","result2rp1a3.csv")
rp.cverror(1008,0.3,"achlioptas","2rp2a3.csv","result2rp2a3.csv")
rp.cverror(1008,0.3,"achlioptas","2rp3a3.csv","result2rp3a3.csv")
rp.cverror(1008,0.3,"achlioptas","2rp4a3.csv","result2rp4a3.csv")
rp.cverror(1008,0.3,"achlioptas","2rp5a3.csv","result2rp5a3.csv")
```
# Achlioptas Dimension:277 Epsilon:0.7
```{r}
set.seed(1)
rp.cverror(277,0.7,"achlioptas","2rp1a7.csv","result2rp1a7.csv")
rp.cverror(277,0.7,"achlioptas","2rp2a7.csv","result2rp2a7.csv")
rp.cverror(277,0.7,"achlioptas","2rp3a7.csv","result2rp3a7.csv")
rp.cverror(277,0.7,"achlioptas","2rp4a7.csv","result2rp4a7.csv")
rp.cverror(277,0.7,"achlioptas","2rp5a7.csv","result2rp5a7.csv")
```

